### 2018-04-11 includes/experiment.tex
Fixing sticking-out words.
Applying recommendations from rebuttal.

We generated several problem instance suites with \fuzzer{} that made one
solver perform poorly, but not others. These suites are
\theSuites{}. Fig.~\ref{fig:cvc-hard} shows the suites that were
uniquely difficult for \cvc{}. Fig.~\ref{fig:z3str3-hard} shows the
suites that were uniquely difficult for \us{}. All experiments were
conducted in series, each with a timeout of 15 seconds,
on an Ubuntu Linux 16.04 computer with 32GB of RAM and an
Intel\textregistered{} Core\texttrademark{} i7-6700 CPU (3.40GHz).
\begin{figure}[h]
    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{data/graphs/concats-extracts-small.png}
        \caption{Performance on \textit{Concats-Extracts-Small}}
        \label{fig:concats-extracts-small}
    \end{subfigure}
    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{data/graphs/different-prefix.png}
        \caption{Performance on \textit{Different-Prefix}}
        \label{fig:different-prefix}
    \end{subfigure}
    \caption{Instances hard for \cvc{}}
    \label{fig:cvc-hard}
    \bigskip
    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{data/graphs/concats-balanced.png}
        \label{fig:concats-balanced}
        \caption{Performance on \textit{Concats-Balanced}}
    \end{subfigure}
    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{data/graphs/concats-big.png}
        \label{fig:concats-big}
        \caption{Performance on \textit{Concats-Big}}
    \end{subfigure}
    \caption{Instances hard for \us{}}
    \label{fig:z3str3-hard}
\end{figure}

>>>>

We generated several problem instance suites with \fuzzer{} that made one
solver perform poorly, but not others.\footnote{Only the
results that made one solver perform poorly and not others are presented, but
results for all \fuzzer{} suites are available on the \fuzzer{} website.}
They are \theSuites{}. Fig.~\ref{fig:cvc-hard} shows the suites that were
uniquely difficult for \cvc{}. Fig.~\ref{fig:z3str3-hard} shows the
suites that were uniquely difficult for \us{}. All experiments were
conducted in series, each with a timeout of 15 seconds,
on an Ubuntu Linux 16.04 computer with 32GB of RAM and an
Intel\textregistered{} Core\texttrademark{} i7-6700 CPU (3.40GHz).
\begin{figure}[h]
    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{data/graphs/concats-extracts-small.png}
        \caption{Performance on \textit{Concats-Extracts-Small}}
        \label{fig:concats-extracts-small}
    \end{subfigure}
    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{data/graphs/different-prefix.png}
        \caption{Performance on \textit{Different-Prefix}}
        \label{fig:different-prefix}
    \end{subfigure}
    \caption{Instances hard for \cvc{}}
    \label{fig:cvc-hard}
    \bigskip
    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{data/graphs/concats-balanced.png}
        \label{fig:concats-balanced}
        \caption{Performance on \textit{Concats-Balanced}}
    \end{subfigure}
    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{data/graphs/concats-big.png}
        \label{fig:concats-big}
        \caption{Performance on \textit{Concats-Big}}
    \end{subfigure}
    \caption{Instances hard for \us{}}
    \label{fig:z3str3-hard}
\end{figure}

### 2018-04-11 includes/stringfuzz.tex
Applying recommendations from rebuttal.

\subsubsection{Regex Generating Capabilities}
\fuzzer{} can generate
and transform instances with regular expression constraints. For example,
\texttt{stringfuzzg regex} invokes the regex
generator and produces an instance of the form:
\begin{align*}
    & \texttt{(assert (str.in.re X}\; R_0\; \texttt{))} \\
    & \texttt{(assert (str.in.re X}\; R_n\; \texttt{))}* \\
    & \texttt{(assert (<= Min (str.len X)))}? \\
    & \texttt{(assert (<= (str.len X)) Max)}?
\end{align*}

\noindent where $R_i \in RegEx$, and $Min, Max \in Int$. More simply, the
instance is a set of one or more regex constraints on a single
variable, with optional maximum and minimum length constraints. The
regex constraints $R$ are each of the form:
\begin{align*}
    & \texttt{(re.++}\; T_0\; \texttt{(re.++}\; T_1\;
    \texttt{...}\; \texttt{(re.++}\; T_{n-1}\; T_n\; \texttt{))}
\end{align*}

\noindent and each $T_i$ is a recursive term of the form:
\begin{align*}
    & \texttt{(re.*}\; T_{i_j}\; \texttt{) | (re.+}\; T_{i_j}\;
    \texttt{) | (re.union}\; T_{i_{j_1}}\; T_{i_{j_2}}\; \texttt{)}
\end{align*}

\noindent where $j$ is the specified depth of recursion. Terms at depth 0 are
regex constants. Informally, this form describes a concatenation of
regex terms, where each term is a random nested regex operator (chosen from
regex Kleene star, repetition, and union), up to a specified depth,
terminating in a regex literal. Below are three example regex instances
(separated by spaces) of depth 2 produced by this scheme:
\begin{align*}
    & ((\texttt{a}|\texttt{b})|(\texttt{cc})+)\quad\quad
    ((\texttt{ddd})*)+\quad\quad ((\texttt{ee})+|(\texttt{fff})*)
\end{align*}

>>>>

\subsubsection{Regex Generating Capabilities}

\fuzzer{} can generate and transform instances with regex
constraints. For example, the command
``\texttt{stringfuzzg regex -r 2 -d 1 -t 1 -M 3 -X 10}'' produces this instance:
{\small\begin{verbatim}        (set-logic QF_S)
        (declare-fun var0 () String)
        (assert (str.in.re var0 (re.+ (str.to.re "R5"))))
        (assert (str.in.re var0 (re.+ (str.to.re "!PC"))))
        (assert (<= 3 (str.len var0)))
        (assert (<= (str.len var0) 10))
        (check-sat)\end{verbatim}}

Each instance is a set of one or more regex constraints on a single
variable, with optional maximum and minimum length constraints. Each regex
constraint is a concatenation (\texttt{re.++} in SMT-LIB string syntax)
of regex terms:
\begin{align*}
    & \texttt{(re.++ T1 (re.++ T2} \; ... \; \texttt{(re.++ Tn-1 Tn )))}
\end{align*}

\noindent and each term is recursively defined as any one of: repetition
(\texttt{re.*}), Kleene star (\texttt{re.+}), union (\texttt{re.union}), or a
character literal. Nested operators are nested up to a specified depth of
recursion. Terms at depth 0 are always regex constants.

Intuitively, each instance is a concatenation of regex terms, where each
term is a random nested regex operator with random arguments
(up to a specified depth) terminating in a regex literal.
Below are three example regexes (in regex syntax, not in the SMT-LIB language)
of depth 2 that can be produced by this scheme:
\begin{align*}
    & ((\texttt{a}|\texttt{b})|(\texttt{cc})+)\quad\quad\quad
    ((\texttt{ddd})*)+\quad\quad\quad ((\texttt{ee})+|(\texttt{fff})*)
\end{align*}

### 2018-04-11 includes/suites.tex
Applying recommendations from rebuttal.

\begin{table}[t]
    \caption{Repository of 10,258 \smtfull{} instances.}
    \begin{subtable}{1\textwidth}
        \centering
        \caption{\generator{}-generated instances.}
        \label{tbl:generated}
        \begin{tabular}{llr}
            \toprule
            \textbf{Name}
                & \textbf{Instances have a ...}
                & \textbf{Quantity}
            \\
            \midrule
            \textit{Concats}
                & Right-heavy, deep tree of concats.
                & 120 \\
            \textit{Concats-Balanced}
                & Balanced, deep tree of concats.
                & 100 \\
            \textit{Concats-Extracts}
                & Single concat tree, with character extractions.
                & 120 \\
            \textit{Lengths}
                & Single, large length constraint on a variable.
                & 200 \\
            \textit{Lengths-Concats}
                & Tree of fixed-length concats of variables.
                & 100 \\
            \textit{Overlaps}
                & Formula of the form A.X = X.B.
                & 80 \\
            \textit{Regex}
                & Complex regex membership test.
                & 120 \\
            \textit{Many-Regexes}
                & Multiple random regex membership tests.
                & 40 \\
            \textit{Regex-Deep}
                & Regex membership test with many nested operators.
                & 45 \\
            \textit{Regex-Pair}
                & Test for membership in one regex, but not another.
                & 40 \\
            \textit{Regex-Lengths}
                & Regex membership test, and a length constraint.
                & 40 \\
            \textit{Different-Prefix}
                & Equality of two deep concats with different prefixes.
                & 60 \\
            \bottomrule
        \end{tabular}
    \end{subtable}

>>>>

\begin{table}[t]
    \caption{Repository of 10,258 \smtfull{} instances.}
    \begin{subtable}{1\textwidth}
        \centering
        \caption{\generator{}-generated instances.}
        \label{tbl:generated}
        \begin{tabular}{llr}
            \toprule
            \textbf{Name}
                & \textbf{Instances have a ...}
                & \textbf{Quantity}
            \\
            \midrule
            \textit{Concats-\{Small,Big\}}
                & Right-heavy, deep tree of concats.
                & 120 \\
            \textit{Concats-Balanced}
                & Balanced, deep tree of concats.
                & 100 \\
            \textit{Concats-Extracts-\{Small,Big\}}
                & Single concat tree, with character extractions.
                & 120 \\
            \textit{Lengths-\{Long,Short\}}
                & Single, large length constraint on a variable.
                & 200 \\
            \textit{Lengths-Concats}
                & Tree of fixed-length concats of variables.
                & 100 \\
            \textit{Overlaps-\{Small,Big\}}
                & Formula of the form A.X = X.B.
                & 80 \\
            \textit{Regex-\{Small,Big\}}
                & Complex regex membership test.
                & 120 \\
            \textit{Many-Regexes}
                & Multiple random regex membership tests.
                & 40 \\
            \textit{Regex-Deep}
                & Regex membership test with many nested operators.
                & 45 \\
            \textit{Regex-Pair}
                & Test for membership in one regex, but not another.
                & 40 \\
            \textit{Regex-Lengths}
                & Regex membership test, and a length constraint.
                & 40 \\
            \textit{Different-Prefix}
                & Equality of two deep concats with different prefixes.
                & 60 \\
            \bottomrule
        \end{tabular}
    \end{subtable}
